Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-02-22 resex.tex
Revised Section III on residual kicks. Added 2 references to resex-bibtex.bib. Including PDF paper in this commit.

\subsection{Uncompensated kicks from injection and extraction bends}
\label{core:sec:1}

@@

\subsection{Kicks in the central region (main solenoid)}
\label{core:sec:2}

For a perfectly annular and axially symmetric profile, the field in
the region of the proton beam core vanishes. This is expressed by
Eq.~\ref{eq:field_2} and is illustrated in
Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam
core can arise in case of profile imperfections of the electron
beam, in particular if the axial symmetry is broken.

@@

In the test stand, only resistive solenoids are available. Through
simulations, one can estimate the fields generated by the compressed
electron beam profile needed for HL-LHC. The measured distribution is
compressed to the inner electron beam radius of 1.24~mm, corresponding
to $4\sigma_p$, as described in Table~\ref{tab:hllhc_param} and
Table~\ref{tab:hel_param}. A distribution with about $65\,000$
particles is generated according to the measured current-density
profile. As boundary condition, the LHC inner beam pipe radius
$b=30$~mm is used. The potential and fields are then calculated with
the particle-in-cell code Warp~\cite{warp}. The resulting relative
electric field strengths are shown in Fig.~\ref{core:fig:1}. The
electric field is obviously proportional to the charge density of
electrons. Its relative strength is rather insensitive to the hollow
beam radii, as long as these remain small compared to the beam pipe
radius. Further details on the measurements and Warp simulations can
be found in Ref.~\cite{hel_res_field_stancari_2017}.

Using these measurements and calculations of the relative electric
field strengths in the transverse plane (Fig.~\ref{core:fig:1}), we
obtain an average field in the hole of

\begin{equation}
  E_{\mathrm{rel}}= 5\%.
\end{equation}

For a maximum kick of 392~nrad, as derived in Eq.~\ref{eqn:helkick},
the estimated dipole kick amplitude at the proton beam core is then

\begin{equation}
  \label{eqn:kick_central}
  \Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} = \q{20}{nrad}.
\end{equation}

For the scope of this paper, only the approximate magnitude of the
residual dipole kick is considered. In general, the field map,
including its multipolar components, can be parameterized in a
symplectic form, as described for instance in
Ref.~\cite{hel_bends_stancari}, and used in tracking codes to estimate
the effects on the circulating beam.

>>>>

\subsection{Kicks from injection and extraction bends}
\label{core:sec:1}

@@

\subsection{Kicks in the central overlap region}
\label{core:sec:2}

For a perfectly annular and axially symmetric electron beam profile,
the electromagnetic field in the region of the proton beam core
vanishes. This is expressed by Eq.~\ref{eq:field_2} and is illustrated
in Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam
core can arise if the axial symmetry is broken.

@@

In the test stand, only resistive solenoids are available. One can
estimate the fields generated by the compressed electron beam profile
in the superconducting solenoids of the HL-LHC HEL using a combination
of experimental measurements and calculations.

Experimentally, it was verified that the current-density profiles
scale with electron beam current and confining axial field according
to space-charge evolution~\cite{Jo:PoP:2018,
  hel_res_field_stancari_2017}. Specifically, the same profile is
obtained for a given family of experimental conditions with constant
ratio $\sqrt{V} / B$, where $V$ is the accelerating voltage and $B$ is
the axial field. This ratio is proportional to the space-charge
evolution number $g = \omega_D \cdot \tau \propto \sqrt{V}/B$,
representing the number of $\vec{E} \times \vec{B}$ rotations in the
propagation time~$\tau$, with
$\omega_D \equiv \omega_p^2 / (2 \omega_c)$ the diocotron frequency,
$\omega_p$ the plasma frequency, and $\omega_c$ the cyclotron
frequency of the magnetically confined electrons in the
solenoid~\cite{Davidson:nonneutral-plasmas:2001}.

For a given HL-LHC HEL configuration, the corresponding
current-density profile measured in the Fermilab test stand is used as
input to calculate the electromagnetic fields. For the purpose of
estimating the residual fields, the measured distribution is
compressed to the inner electron beam radius of 1.24~mm, corresponding
to $4\sigma_p$, as described in Table~\ref{tab:hllhc_param} and
Table~\ref{tab:hel_param}. A distribution with about $65\,000$
particles is generated according to the measured current-density
profile. As boundary condition, the LHC inner beam pipe radius
$b = \q{30}{mm}$ is used. The potential and fields are then calculated
with Warp~\cite{warp}. The resulting relative electric field strengths
are shown in Fig.~\ref{core:fig:1}. The electric field is obviously
proportional to the charge density of electrons. Its relative strength
is rather insensitive to the hollow beam radii, as long as these
remain small compared to the beam pipe radius. Further details on the
measurements and Warp simulations can be found in
Ref.~\cite{hel_res_field_stancari_2017}.

Using these measurements and calculations of the relative electric
field strengths in the transverse plane (Fig.~\ref{core:fig:1}), we
obtain a median field in the hole of
%
\begin{equation}
  \langle E_\mathrm{hole} \rangle / E_\mathrm{max} =  5\%.
\end{equation}
%
For a maximum kick of 392~nrad, as derived in Eq.~\ref{eqn:helkick},
the estimated dipole kick amplitude at the proton beam core is therefore
approximately
%
\begin{equation}
  \label{eqn:kick_central}
  \Delta x' , \Delta y' = \q{20}{nrad}.
\end{equation}
%
The relative magnitude of the residual field depends on several
factors, including cathode quality, electron gun geometry, solenoid
field configuration, space-charge evolution, etc. It can be improved,
if needed.

For the purposes of this paper, only the approximate magnitude of the
residual dipole kick is considered. In general, the field map,
including its multipolar components, can be parameterized in
symplectic form, as described for instance in
Ref.~\cite{hel_bends_stancari}, and used in tracking codes to estimate
the effects on the circulating beam.
